The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-07-29 Paper/jaccardbaetica.tex
add parrafo intro corr xavi

@@

The approach proposed here aimed at exploring links between production and consumption centers through the identification of common amphorae codes found in different sites. For this reason we measured the similarity between amphora workshops and/or consumption sites by quantifying a pairwise distance or dissimilarity index between places (i.e. to what extent the stamp codes found on these sites were different). The chosen dissimilarity measure was the Morisita-Horn index \citep{morisita_measuring_1959, horn_measurement_1966}. This method was applied to measure the dissimilarity between different samples of sets. Generally, it describes the dissimilarity between the system of two communities based on the idea of inverse correlation between diversity and species \citep{magurran_why_1988}\xavi{citar reforzar más esta idea}.

>>>>

This work focuses on the debate about the dynamics of the distribution of olive oil market in Roman provinces. Amphoric production in Baetica province will help us to identify links between production centres and consumption centres in order to detect an economic pattern in the commerce by analysing stamps amphorae finding in the provinces.

The finding of amphoric stamps in different provinces has allowed us to know the importance of the distribution of olive oil within the Empire. Despite having archaeological evidence, no consensus has been reached: How was the economical relation between production and consumption centers? Did they follow a economical pattern to distribute olive oil in those provinces?

@@

The approach proposed here aimed at exploring links between production and consumption centers through the identification of common amphorae codes found in different sites. For this reason we measured the similarity between amphora workshops and/or consumption sites by quantifying a pairwise distance or dissimilarity index between places (i.e. to what extent the stamp codes found on these sites were different). The chosen dissimilarity measure was the Morisita-Horn index \citep{morisita_measuring_1959, horn_measurement_1966}. This method was applied to measure the dissimilarity between different samples of sets. Generally, it describes the dissimilarity between the system of two communities based on the idea of inverse correlation between diversity and species \citep{magurran_why_1988}. In our case, stamps from different sites will be used as a proxy to measure their dissimilarity by analyzing their code. 
\xavi{citar reforzar más esta idea}.
\maria{he añadido unas líneas a ver si están bien o no xD}
